---
title       : Slidify Presentation
subtitle    : Coursera Data Product Course Project Part 2
author      : Gopal D Bhatta
job         : July 21, 2016
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

---

Introduction

This is a reproducible pitch presentation using slidify. This part uses mtcars dataset from one of the available datasets in R. 
Few next slides shows the structure of the variables and sample data.

---

Structure of the dataset
```{r, echo = TRUE}
library(datasets)
str(mtcars)
```

---

Sample Data
```{r, echo = TRUE}
head(mtcars)
```
The source codes for ui.R and server.R files are available on github. 

---

The Application

The (mtcars) database is used for the application. The link to the application is https://gopalbhatta.shinyapps.io/data_mtcars/

The app allows to perform interactive data analysis from a set of user specified criteria- 

The selling price of gasoline (US $/gallon) and desired travel distance.

